---
title: "Part2project"
author: "Simone Van Taylor"
date: "8/11/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lets Load In and Explore the Data!!

```{r echo = FALSE}
library(ggplot2)
library(magrittr)
library(tidyverse)
```


```{r ToothGrowth}
#load in data
toothgrowth <- ToothGrowth
#explore the data 
head(toothgrowth)
unique(toothgrowth$supp)
unique(toothgrowth$dose)
summary(toothgrowth)
#whats the mean of the toothgrowth by supplement? 
toothgrowth %>% 
  group_by(supp) %>%
  summarise(mean(len))

##seems like its a little longer for OJ 

##whats the mean by dose? 
toothgrowth %>% 
  group_by(dose) %>%
  summarise(mean(len))
```
seems like the higher the dose the better 

## Lets Visualize this Exploratory Analysis

```{r}
#lets visualize this: 
toothgrowth %>%
  ggplot(aes(x = as.factor(dose), y = len, fill = supp))+ 
  geom_boxplot()+ 
  labs(xlab = "dose", ylab = "length", title = "Tooth Length vs Dose by Delivery")
```
looks like theres a basic trend that as dose goes up length goes up. But is it significant? and is there an effect of supplement?

##T Tests 
```{r}
t.test(len~supp, data = toothgrowth)
```
confidence interval crosses 0 and p is not less than .05 therefore we fail to reject the null hypothesis. Looks to be no significant difference between supplement type 


```{r}
toothgrowth_sub <- filter(ToothGrowth, ToothGrowth$dose == 1.0|ToothGrowth$dose == 0.5)
t.test(len~dose,data=toothgrowth_sub)

toothgrowth_sub <- filter(ToothGrowth, ToothGrowth$dose == 0.5|ToothGrowth$dose == 2.0)
t.test(len~dose,data=toothgrowth_sub)

toothgrowth_sub <- filter(ToothGrowth, ToothGrowth$dose == 1.0|ToothGrowth$dose == 2.0)
t.test(len~dose,data=toothgrowth_sub)
```
for all t tests the confidence int did not pass through zero and p was less than .05 therefore we reject the null hypothesis and can conclude dose significantly effected tooth length